A Tale of Two Transects

### 2020-02-10 writing/transect_paper.Rmd
combine venn diagram calculations into a function

```{r venn-table-asv}
loadd(venn_ASV, cache = cache)

linesep <- venn_ASV %>%
  filter(!is.na(ASVs)) %>%
  select(starts_with("reads")) %>%
  mutate_all(nchar) %>%
  as.matrix %>%
  is_greater_than(0) %>%
  rowSums %>%
  rle() %$%
  map(lengths, ~ c(rep("", . - 1), "\\addlinespace")) %>%
  unlist() %>%
  head(length(.) - 2) %>%
  c("\\midrule")
empty_background = if (options("knitr.table.format") == "html") "#777777" else "gray"
venn_ASV %>%
  rownames_to_column(" ") %>%
  filter(!is.na(ASVs)) %>%
  mutate_all(~ifelse(
    . == "",
    kableExtra::cell_spec("  ", background = empty_background, background_as_tile = FALSE), .)) %>%
  mutate_at(" ", str_replace, "[01]+", "") %>%
  set_names(gsub("_[[:alpha:]]+[-._]\\d+$", "", names(.))) %>%
  set_names(gsub("_", " ", names(.))) %>%
  kable(
    booktabs = TRUE,
    caption = "(ref:venn-table-asv)",
    linesep = linesep,
    align = ("rcrrcrrcrr"),
    row.names = FALSE,
    escape = FALSE
  ) %>%
  kableExtra::add_header_above(
    header = c(
      " " = 2,
      names(venn_ASV)[-(1)] %>% 
        gsub(pattern = "(ASV_)?(reads|frac)_", replacement = "") %>%
        rle() %$%
        set_names(lengths, plyr::mapvalues(values, datasets$seq_run, datasets$amplicon, FALSE))
      )
  ) %>%
  kableExtra::add_header_above(
    header = c(
      " " = 2,
       names(venn_ASV)[-(1)] %>% 
        gsub(pattern = "(ASV_)?(reads|frac)_", replacement = "") %>%
        plyr::mapvalues(datasets$seq_run, paste(datasets$tech, datasets$machine), FALSE) %>%
        rle() %$%
        set_names(lengths, values)
      )
  )
```

@@

```{r venn-table-otu}
loadd(venn_OTU, cache = cache)

linesep <- venn_OTU %>%
  filter(!is.na(OTUs)) %>%
  select(starts_with("reads")) %>%
  mutate_all(nchar) %>%
  as.matrix %>%
  is_greater_than(0) %>%
  rowSums %>%
  rle() %$%
  map(lengths, ~ c(rep("", . - 1), "\\addlinespace")) %>%
  unlist() %>%
  head(length(.) - 2) %>%
  c("\\midrule")
venn_OTU %>% as.matrix() %>% equals("") %>% which()
venn_OTU %>%
  rownames_to_column(" ") %>%
  filter(!is.na(OTUs)) %>%
  mutate_all(~ifelse(
    . == "",
    kableExtra::cell_spec(
      "  ",
      background = empty_background,
      background_as_tile = FALSE
    ),
    .)) %>%
  mutate_at(" ", str_replace, "[01]+", "") %>%
  set_names(gsub("_[[:alpha:]]+[-._]\\d+$", "", names(.))) %>%
  set_names(gsub("_", " ", names(.))) %>%
  kable(
    booktabs = TRUE,
    caption = "(ref:venn-table-otu)",
    linesep = linesep,
    align = ("rcrrcrrcrrcrr"),
    row.names = FALSE,
    escape = FALSE
  ) %>%
  kableExtra::add_header_above(
    header = c(
      " " = 2,
      names(venn_OTU)[-1] %>% 
        gsub(pattern = "(OTU_)?(reads|frac)_", replacement = "") %>%
        rle() %$%
        set_names(lengths, plyr::mapvalues(values, datasets$seq_run, datasets$amplicon, FALSE))
      )
  ) %>%
  kableExtra::add_header_above(
    header = c(
     " " = 2,
      names(venn_OTU)[-1] %>% 
        gsub(pattern = "(OTU_)?(reads|frac)_", replacement = "") %>%
        plyr::mapvalues(datasets$seq_run, paste(datasets$tech, datasets$machine), FALSE) %>%
        rle() %$%
        set_names(lengths, values)
      )
  ) %>%
  kableExtra::landscape()
```

@@

```{r venn, fig.cap = "(ref:venn)", out.height = "30%", fig.show="hold"}
vennplot_ASV <- venn_ASV %>%
  rownames_to_column("set") %>%
  filter(set != "Total") %>%
  mutate(set = map_chr(set,
                       ~ strsplit(., "")[[1]] %>%
                     as.integer() %>%
                     as.logical() %>%
                     magrittr::extract(LETTERS[seq_along(.)], .) %>%
                     paste(collapse = "&"))) %>%
  mutate(
    reads_frac = paste(frac_pb_500, frac_pb_483, frac_is_057, `frac_SH-2257`,
                       sep = "/") %>%
      gsub("/+", "/", .) %>%
      gsub("(^/|/$)", "", .),
    label = str_c(ASVs, reads_frac, sep = "\n") %>%
      replace_na("-")
  )

eulerr::venn(deframe(select(vennplot_ASV, set, ASVs)) %>% replace_na(0)) %>%
  plot(
    legend = list(
      labels = c("PacBio Long", "PacBio Short", "Ion Torrent", "Illumina")
    ),
    quantities = vennplot_ASV$label,
    main = "ASV",
    gp = grid::gpar(cex = 0.8)
  )

vennplot_OTU <- venn_OTU %>%
  rownames_to_column("set") %>%
  filter(set != "Total") %>%
  mutate(set = map_chr(set,
                       ~ strsplit(., "")[[1]] %>%
                     as.integer() %>%
                     as.logical() %>%
                     magrittr::extract(LETTERS[seq_along(.)], .) %>%
                     paste(collapse = "&"))) %>%
  mutate(
    reads_frac = paste(frac_pb_500, frac_pb_483, frac_is_057, `frac_SH-2257`,
                       sep = "/") %>%
      gsub("/+", "/", .) %>%
      gsub("(^/|/$)", "", .),
    label = str_c(OTUs, reads_frac, sep = "\n") %>%
      replace_na("-")
  )

eulerr::venn(deframe(select(vennplot_OTU, set, OTUs)) %>% replace_na(0)) %>%
  plot(
    legend = FALSE,
    labels = FALSE,
    quantities = vennplot_OTU$label,
    main = "OTU",
    gp = grid::gpar(cex = 0.6)
  )

>>>>

```{r venn-table-asv}
readd(venn_ASV, cache = cache) %>%
venn_table(ASVs, "(ref:venn-table-asv)")
```

@@

```{r venn-table-otu}
readd(venn_OTU, cache = cache) %>%
venn_table(OTUs, "(ref:venn-table-otu)")
```

@@

```{r venn, fig.cap = "(ref:venn)", out.height = "30%", fig.show="hold"}
readd(vennplot_ASV, cache = cache) %>% {
  plot(
    select(., set, ASVs) %>% deframe() %>% replace_na(0) %>% eulerr::venn(),
    legend = list(
      labels = c("PacBio Long", "PacBio Short", "Ion Torrent", "Illumina")
    ),
    quantities = .$label,
    main = "ASV"
  )
}

readd(vennplot_OTU, cache = cache) %>% {
  plot(
    select(., set, OTUs) %>% deframe() %>% replace_na(0) %>% eulerr::venn(),
    legend = FALSE,
    labels = FALSE,
    quantities = .$label,
    main = "OTU"
  )
}
